LSOA domestic Electricty and Gas maps

### 2021-09-16 LSOA domestic Elec and Gas.Rmd
Error with age again elec consumption

@@

# plotting the gas consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = mean_dg2019)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Winchester")
```

>>>>

### Plotting over 65s against dom elec consumption 
```{r Loading in the Census age data}
inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
census_age<-readr::read_csv (inFile)
census_age$'LSOA11CD'<- census_age$'geography code'
census_age$prop_65m <- census_age$`Over 65s`/census_age$`Age: All usual residents; measures: Value`
head(census_age)
names(census_age)
message("Original Proportion Over 65:")
summary(census_age$`Proportion Over 65`)
message("New prop_65m:")
summary(census_age$prop_65m)
```
```{r Plotting elec consumption in the over 65s}
#BROKEN
#domelec_LSOA_2019$LSOA11CD <-domelec_LSOA_2019$`Local Authority Name`
#census_age_2019elec <- merge(domelec_LSOA_2019, census_age, by= "LSOA11CD")
#head(census_age_2019elec)
#Select varibale we want
#aggec_2019 <- dplyr::select(census_age_2019elec, LSOA11CD, "Local Authority Name", "Proportion Over 65", mean_de2019, prop_65m )
#head(aggec_2019)

domelec_LSOA_2019$LSOA11CD <- domelec_LSOA_2019$`Lower Layer Super Output Area (LSOA) Name`
Census_age_elec2019 <- merge(domelec_LSOA_2019, census_age, by = "LSOA11CD")
# select the variables we want for clarity

de_age <- dplyr::select(Census_age_elec2019, LSOA11CD, "Local Authority Name",mean_de2019, "Proportion Over 65", prop_65m)
head(de_age)
# table(df$`LA Name`)

de_age$la_name <- de_age$`Local Authority Name` # make a new variable with an easier name
# select the places we want here
getSolent <- function(df){
  # assumes we are filtering on la_name
  res <- dplyr::filter(df, la_name == "Basingstoke and Deane"|
                           la_name == "East Hampshire"|
                           la_name == "Eastleigh"|
                           la_name == "Fareham"|
                           la_name == "Gosport"|
                           la_name == "Hart"|
                           la_name == "Havant"|
                           la_name == "New Forest"|
                           la_name == "Portsmouth"|
                           la_name == "Rushmoor"|
                           la_name == "Southampton"|
                           la_name == "Test Valley"|
                           la_name == "Winchester"|
                           la_name == "Isle of Wight"
                           )
return(res)
}
Solent_2019 <- getSolent(de_age) # use our function to get just Solent LAs
nrow(Solent_2019)
ggplot(Solent_2019, aes(x= 100 * prop_65m, 
                   y= mean_de2019, 
                   colour = la_name)) + # use colour for each LA
  geom_point() +
  geom_smooth() + # adds a smoothed best fit line
  theme(legend.position = "None") + # otherwise we get the colour legend at the side
  labs(x = "% aged > 65, 2011 Census",
       y = "Domestic Electricity COnsumption") +
  facet_wrap(. ~ la_name) # draws a separate plot for each LA (in a different colour)
message("Correlation coeficient across all LSOAs (2019)")
cor(Solent_2019$prop_65m, Solent_2012$mean_de2019)
```

@@

# plotting the gas consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = mean_dg2019)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Winchester")
```
### Plotting gas usage against proportion of over 65s
```{r Loading in the Census age data}
inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
census_age<-readr::read_csv (inFile)
census_age$'LSOA11CD'<- census_age$'geography code'
census_age$prop_65m <- census_age$`Over 65s`/census_age$`Age: All usual residents; measures: Value`
head(census_age)
names(census_age)
message("Original Proportion Over 65:")
summary(census_age$`Proportion Over 65`)
message("New prop_65m:")
summary(census_age$prop_65m)
```

```{r Graphing over 65s against gas consumption}
#census_age$"LSOA11CD" <- census_age$"geography code"
domgas_LSOA_2019$`Lower Layer Super Output Area (LSOA) Code` <- domgas_LSOA_2019$`LSOA Code`

Census_age_2012fp <- merge(domgas_LSOA_2019, census_age, by = "Lower Layer Super Output Area (LSOA) Code")
# select the variables we want for clarity
df_2012 <- dplyr::select(Census_age_2012fp, LSOA11CD, "LA Name", "Proportion of households fuel poor (%)", "Proportion Over 65", prop_65m)
head(df_2012)
# table(df$`LA Name`)
df_2012$la_name <- df_2012$`LA Name` # make a new variable with an easier name
df_2012$pcFuelPoor <- df_2012$`Proportion of households fuel poor (%)` # same - this is actually a % not a proportion!
# select the places we want here
getSolent <- function(df){
  # assumes we are filtering on la_name
  res <- dplyr::filter(df, la_name == "Basingstoke and Deane"|
                           la_name == "East Hampshire"|
                           la_name == "Eastleigh"|
                           la_name == "Fareham"|
                           la_name == "Gosport"|
                           la_name == "Hart"|
                           la_name == "Havant"|
                           la_name == "New Forest"|
                           la_name == "Portsmouth"|
                           la_name == "Rushmoor"|
                           la_name == "Southampton"|
                           la_name == "Test Valley"|
                           la_name == "Winchester"|
                           la_name == "Isle of Wight"
                           )
return(res)
}
Solent_2012 <- getSolent(df_2012) # use our function to get just Solent LAs
nrow(Solent_2012)
ggplot(Solent_2012, aes(x= 100 * prop_65m, 
                   y= pcFuelPoor, 
                   colour = la_name)) + # use colour for each LA
  geom_point() +
  geom_smooth() + # adds a smoothed best fit line
  theme(legend.position = "None") + # otherwise we get the colour legend at the side
  labs(x = "% aged > 65, 2011 Census",
       y = "% households in fuel poverty, 2012") +
  facet_wrap(. ~ la_name) # draws a separate plot for each LA (in a different colour)
message("Correlation coeficient across al LSOAs (2012)")
cor(Solent_2012$prop_65m, Solent_2012$pcFuelPoor)
```
